### 2020-07-20 article.tex
Two amendments

   \caption{Performance of the matrix--matrix multiplication different sparse matrix formats.\label{fig:perfAX}}

@@

Results are gathered
in~\cref{tab:lobpcg}. In the first row, the numbers of outer LOBPCG iterations
are reported with the three different inner preconditioners mentioned above.
\pk{PCASM} is known to yield a preconditioned operator whose condition number
grows as the number of subdomains, here processes, increases. Thus, the number
of outer iterations is higher than with \pk{PCHPDDM} or \pk{PCGAMG} since the
inner solves are not converging to meaningful solutions in just 5 iterations.
On the other hand, both multilevel preconditioners perform similarly, with a minimal difference in the
number of outer iterations. The second and third rows record
the number of times \pk{PCApply} and \pk{PCMatApply} are called. Since
\pk{PCGAMG} does not handle blocking, at each pseudo-block GMRES iteration,
\pk{PCApply} is called for each active column separately. \pk{PCASM} and
\pk{PCHPDDM} handle blocking, so the only rely on \pk{PCMatApply}. In the fourth
row, the time spent setting up the preconditioners is given. \pk{PCASM} is
extremely cheap but not very robust numerically, while both multilevel
preconditioners have a similar setup time. The
time spent in the full eigenvalue solver is reported in the last row. Clearly, having both a \pk{KSP}
and a \pk{PC} which can efficiently deal with multiple vectors is mandatory to
achieve reasonable performance with such an outer solver that heavily relies on
blocking.
\pgfplotstableread{
PC       outer PCApply PCMatApply PCSetUp       EPSSolve
PCASM    54    ---     378        2.8536e+00    265.6564
PCHPDDM  14    ---     98         2.1566e+01    121.584
PCGAMG   15    4{,}049    ---     2.6528e+01    391.822
}\mytable
\pgfplotstabletranspose[
    colnames from=PC,
    input colnames to=PC
]\mytablenew{\mytable}
\begin{table}[h!]
\caption{Performance of \pk{EPSLOBPCG} with three different inner preconditioners: \pk{PCASM} and \pk{PCHPDDM}, which utilize \pk{PCMatApply}, and \pk{PCGAMG}, which utilizes \pk{PCApply}.\label{tab:lobpcg}}
    \centering
\pgfplotstabletypeset[
columns/PCHPDDM/.style={
postproc cell content/.append code={%
\ifnum\pgfplotstablerow>2
\pgfkeyssetvalue{/pgfplots/table/@cell content}{\pgfmathparse{##1<100?"0":{}}\phantom{\pgfmathresult}\pgfmathparse{##1<10?"0":{}}\phantom{\pgfmathresult}\pgfmathprintnumber[precision=1,fixed]{##1}}%
\fi
}
},
columns/PCGAMG/.style={
postproc cell content/.append code={%
\ifnum\pgfplotstablerow>2
\pgfkeyssetvalue{/pgfplots/table/@cell content}{\pgfmathparse{##1<100?"0":{}}\phantom{\pgfmathresult}\pgfmathparse{##1<10?"0":{}}\phantom{\pgfmathresult}\pgfmathprintnumber[precision=1,fixed]{##1}}%
\fi
}
},
columns/PCASM/.style={
postproc cell content/.append code={%
\ifnum\pgfplotstablerow>2
\pgfkeyssetvalue{/pgfplots/table/@cell content}{\pgfmathparse{##1<100?"0":{}}\phantom{\pgfmathresult}\pgfmathparse{##1<10?"0":{}}\phantom{\pgfmathresult}\pgfmathprintnumber[precision=1,fixed]{##1}}%
\fi
}
},
columns/PC/.style={
    column name={},
% stupid example for multiple postprocessors:
postproc cell content/.append style={
/pgfplots/table/@cell content/.add={\tt}{},
},
postproc cell content/.append code={%
\ifnum\pgfplotstablerow=0
\pgfkeyssetvalue{/pgfplots/table/@cell content}{\# of outer iterations}%
\else
\ifnum\pgfplotstablerow>2
\pgfkeyssetvalue{/pgfplots/table/@cell content}{\pk{##1} (sec)}%
\fi
\fi
}
},
    every even row/.style={
before row={\rowcolor[gray]{0.9}}},
        assign column name/.style={/pgfplots/table/column name={\pk{#1}}},
    every head row/.style={
        before row=\toprule,
        after row=\midrule
    },
    every last row/.style={
        after row=\bottomrule
    },
string type]{\mytablenew}
\end{table}

>>>>

   \caption{Performance of the matrix--matrix multiplication for different sparse matrix formats.\label{fig:perfAX}}

@@

Results are gathered
in~\cref{tab:lobpcg}. In the first row, the numbers of outer LOBPCG iterations
are reported with the three different inner preconditioners mentioned above.
\pk{PCASM} is known to yield a preconditioned operator whose condition number
grows as the number of subdomains, here processes, increases. Thus, the number
of outer iterations is higher than with \pk{PCHPDDM} or \pk{PCGAMG} since the
inner solves are not converging to meaningful solutions in just 5 iterations.
On the other hand, both multilevel preconditioners perform similarly, with a minimal difference in the
number of outer iterations. The second and third rows record
the number of times \pk{PCApply} and \pk{PCMatApply} are called. Since
\pk{PCGAMG} does not handle blocking, at each pseudo-block GMRES iteration,
\pk{PCApply} is called for each active column separately. \pk{PCASM} and
\pk{PCHPDDM} handle blocking, so they only rely on \pk{PCMatApply}. In the fourth
row, the time spent setting up the preconditioners is given. \pk{PCASM} is
extremely cheap but not very robust numerically, while both multilevel
preconditioners have a similar setup time. The
time spent in the full eigenvalue solver is reported in the last row. Clearly, having both a \pk{KSP}
and a \pk{PC} which can efficiently deal with multiple vectors is mandatory to
achieve reasonable performance with such an outer solver that heavily relies on
blocking.
\pgfplotstableread{
PC       outer PCApply PCMatApply PCSetUp       EPSSolve
PCASM    54    ---     378        2.8536e+00    265.6564
PCHPDDM  14    ---     98         2.1566e+01    121.584
PCGAMG   15    4{,}049    ---     2.6528e+01    391.822
}\mytable
\pgfplotstabletranspose[
    colnames from=PC,
    input colnames to=PC
]\mytablenew{\mytable}
\begin{table}[h!]
\caption{Performance of \pk{EPSLOBPCG} with three different inner preconditioners: \pk{PCASM} and \pk{PCHPDDM}, which utilize \pk{PCMatApply}, and \pk{PCGAMG}, which utilizes \pk{PCApply}.\label{tab:lobpcg}}
    \centering
\pgfplotstabletypeset[
columns/PCHPDDM/.style={
postproc cell content/.append code={%
\ifnum\pgfplotstablerow>2
\pgfkeyssetvalue{/pgfplots/table/@cell content}{\pgfmathparse{##1<100?"0":{}}\phantom{\pgfmathresult}\pgfmathparse{##1<10?"0":{}}\phantom{\pgfmathresult}\pgfmathprintnumber[precision=1,fixed]{##1}}%
\fi
}
},
columns/PCGAMG/.style={
postproc cell content/.append code={%
\ifnum\pgfplotstablerow>2
\pgfkeyssetvalue{/pgfplots/table/@cell content}{\pgfmathparse{##1<100?"0":{}}\phantom{\pgfmathresult}\pgfmathparse{##1<10?"0":{}}\phantom{\pgfmathresult}\pgfmathprintnumber[precision=1,fixed]{##1}}%
\fi
}
},
columns/PCASM/.style={
postproc cell content/.append code={%
\ifnum\pgfplotstablerow>2
\pgfkeyssetvalue{/pgfplots/table/@cell content}{\pgfmathparse{##1<100?"0":{}}\phantom{\pgfmathresult}\pgfmathparse{##1<10?"0":{}}\phantom{\pgfmathresult}\pgfmathprintnumber[precision=1,fixed]{##1}}%
\fi
}
},
columns/PC/.style={
    column name={},
% stupid example for multiple postprocessors:
postproc cell content/.append style={
/pgfplots/table/@cell content/.add={\tt}{},
},
postproc cell content/.append code={%
\ifnum\pgfplotstablerow=0
\pgfkeyssetvalue{/pgfplots/table/@cell content}{\# of outer iterations}%
\else
\ifnum\pgfplotstablerow>2
\pgfkeyssetvalue{/pgfplots/table/@cell content}{\pk{##1} (sec)}%
\fi
\fi
}
},
    every even row/.style={
before row={\rowcolor[gray]{0.9}}},
        assign column name/.style={/pgfplots/table/column name={\pk{#1}}},
    every head row/.style={
        before row=\toprule,
        after row=\midrule
    },
    every last row/.style={
        after row=\bottomrule
    },
string type]{\mytablenew}
\end{table}
